

\section{Final Budget}
The final budget was reduced from the proposed cost breakdown since some material that was required for the manufacturing of components was already at Penguin ASI as spare material. Cost that were reduced off the proposed list were the 1" Aluminum plates, 1/4" Aluminum plates, 8"x2"x1/4" Aluminum tubing, and the 2"x2"x1/8" Aluminum L beam and tubing. Water jet cutting of the plates was stated in the design proposal report, but that cost was not applied since we had decided to use the CNC mill provided to us by Penguin ASI. The lead time estimated by Stainless Technologies was two weeks, but we were able to complete the drive box plates at Penguin within one week since we had received help from their machinist. The total cost reduction from the original estimated cost was \$2,494.02 CAD dollars, that is not including the water jet cutting since it was not a method that was not decided upon during the proposal to Penguin ASI. Some of the most expensive components of the design included the belt and both the small and large sprockets. The larger sprockets had a lead time of 4 to 5 weeks but they did not come in until the 8 week mark from BDI. Some parts such as seals and tapered roller bearings were ordered twice and were placed for return to BDI to be refunded. With those reduced costs the final budget comes to \$7,413.01 CAD dollars. This total does not include the cost of machining time along with the cost of the employees wages that had contributed to helping with the project when their assistance was needed. Table\ref{tab:budg_par} shows the cost breakdown for the components and the material that was required to complete the project with the lead times and prices for each.
\begin{landscape}
\begin{longtable}{| $l^l^l^l^l^l^l |} 
\caption[Final budget for Parts]{Final Budget and lead times for purchased parts before taxes and shipping fees.}  \label{tab:budg_pur} \\
%\begin{tabular}{| $p{4cm}^p{3cm}^l^l^l^l^l |} 
\hline
Component & Manufacturer & Supplier & Price/Unit & Quantity & Total  & Lead time\\ \hline
\endfirsthead
\hline
Component & Manufacturer & Supplier & Price/Unit & Quantity & Total  & Lead time\\ \hline
\endhead
 \rowstyle{\bfseries}  Continued... &  &  &  &  &  & \\ \hline
\endfoot
\endlastfoot
Hub O-rings & DAE & BDI & \$0.23 & 8 & \$1.84 & Stock\\
Bearing Housing O-ring & DAE & BDI & \$0.35 & 16 & \$5.60 & Stock\\
Wheel Hub O-ring & DAE & BDI & \$0.35 & 8 & \$2.80 & Stock\\
Pivot O-ring & DAE & BDI & \$0.28 & 12 & \$3.36 & Stock\\
Drive box Custom O-ring & - & BDI & \$17.51 & 16 & \$280.16 & 4 Days\\
 &  &  &  &  &  & \\
Large Sprockets & Martin Sprocket & BDI & \$179.21 & 8 & \$1,433.68 & 4 to 5 Weeks\\
Small Sprockets & Martin Sprocket & BDI & \$101.29 & 4 & \$405.16 & Stock\\
Large Bushing For Sprocket & Martin Sprocket & BDI & \$20.00 & 8 & \$160.00 & Stock\\
Small Bushing For Sprocket & Martin Sprocket & BDI & \$16.31 & 4 & \$65.24 & Stock\\
Belt & Gates & BDI & \$125.00 & 4 & \$500.00 & Stock\\
 &  &  &  &  &  & \\
20 mm Sealed Ball Bearing & Amcan & BDI & \$20.17 & 8 & \$161.36 & Stock\\
45 mm Tapper Roller Bearing & Amcan & BDI & \$12.19 & 16 & \$195.04 & Stock\\
25 mm Tapper Roller Bearing & Amcan & BDI & \$7.00 & 8 & \$56.00 & Stock\\
 &  &  &  &  &  & \\
45 mm Radial Seal & DAE/DMR & BDI & \$1.84 & 8 & \$14.72 & Stock\\
68 mm Radial Seal & DAE/DMR & BDI & \$3.18 & 8 & \$25.44 & Stock\\
60 mm Radial Seal & SKF & BDI & \$26.15 & 8 & \$209.20 & Stock\\
38 mm Radial Seal & SKF & BDI & \$20.00 & 8 & \$160.00 & Stock\\
25 mm Radial Seal & DMR/DAE & BDI & \$1.38 & 4 & \$5.52 & Stock\\
 &  &  &  &  &  & \\
3/8'' - 24 Thread Repair Kit & Recoil & BDI & \$0.00 & 4 & \$0.00 & Stock\\
1/4'' Grease Nipple & - & Rastall & \$0.00 & 4 & \$0.00 & Stock\\
1/4'' Idler Shaft Bolts & - & Rastall & \$0.00 & 8 & \$0.00 & Stock\\
1.25'' Castle Nut & - & Rastall & \$0.00 & 8 & \$0.00 & Stock\\
3/8'' Housing Bolts & - & Rastall & \$0.00 & 32 & \$0.00 & Stock\\
5/16'' Bolts For Drive Box & - & Rastall & \$0.00 & 140 & \$0.00 & Stock\\
3/8: Wingnut For Idler Adjustment & - & Rastall & \$0.00 & 8 & \$0.00 & Stock\\
3/8'' Threaded Rod For Idler & - & Rastall & \$0.00 & 4 & \$0.00 & Stock\\
5/16'' Bolts For Pivot & - & Rastall & \$0.00 & 88 & \$0.00 & Stock\\
 &  &  &  &  &  & \\
Estimated Cost For All Fasteners  & - & - & - & - & \$500.00 & \\
 \rowstyle{\bfseries} &  &  &  & Total: & \$7,149.12 & \\ \hline
 %\end{tabular}
 \end{longtable}
 \end{landscape}
 
 
\begin{table}[htbp]
\centering
\caption[Final Budget for Materials]{Final Budget and lead times for purchased parts before taxes and shipping fees.}
\begin{tabular}{| $p{4cm}^l^l^l^l^l |} \hline
Component & Supplier & Price/Unit & Quantity & Total  & Lead time\\ \hline
2x2x1/8 6061 Aluminum L Beam &  ASA Alloys & \$51.58 & 10 ft & \$51.58 & Stock\\
2x2x1/8 6061 Aluminum Tubing &  ASA Alloys & \$180.87 & 20 ft & \$180.87 & Stock\\
96.5x48.5 x 1'' 6061 Aluminum plate & ASA Alloys & \$947.87 & 2 & \$1,895.74 & Stock\\
96.5x48.5x1/4'' 6061 Aluminum plate & ASA Alloys & \$296.32 & 1 & \$296.32 & Stock\\
8''x 2'' x 1/4'' 6061 Aluminium tubing & ASA Alloys & \$69.51 & 2x[6 ft] & \$69.51 & To be determined\\
Travel limiter stock &  &  &  &  & \\
SAE 660 Bronze tube OD: 4'' 1/4, ID: 3''1/2 & BDI & \$263.89 & 1 ft & \$263.89 & Stock\\
 \rowstyle{\bfseries}  &  &  & Total: & \$2,757.91 & \\ \hline
 \end{tabular}
 \label{tab:budg_par}
 \end{table}